Adaptive Scheduling of Scientific Workflows

### 2024-04-14 main.tex
changed order of subsections
described the implementation in detail (WIP!), taking a break

\subsection{Heuristics}

We consider two variants of HEFT accounting for memory usage, which only
differ in the order they consider tasks to be scheduled.

@@

HEFTM-MM orders tasks as dictated by MinMem.
\AB{Actually, while writing,
I remember that this might be complicated to compute MinMem for the
entire graph, so this might not be a feasible variant, or needs to be updated?}

@@

\smallskip
\noindent{\bf Step 2.} Next, we check the memory constraint on~$p_j$, by computing
$$Res = \curM_j  + m_v + \sum_{u \in Pred(v), u\notin T(p_j)}  \{c_{u,v}\}
+ \sum_{w\in Succ(v)}  \{c_{v,w}\} - \MM_j .$$

$T(p_j)$ is the set of tasks already scheduled on $p_j$; by step 1, their files are
already in the memory of~$p_j$. However, the files from the 
other predecessor tasks must be loaded in memory before executing task~$v$,
as well as $m_v$ and the data generated for all successor tasks.
$Res$ is then checking whether there was enough memory; if it is positive, 
it means that we have exceeded the memory of~$p_j$ with this tentative 
assignment.

In this case ($Res >0$), we  try evicting
some data from memory so that we have enough memory to execute task~$v$. 
We need to evict at least $Res$ data. For now, we propose a greedy approach,
evicting the smallest files of $\PD_j$ until $Res$ data has been evicted,
in order to avoid costly communications. 
\AB{FYI We initially discussed  evicting the largest files, but this leads to 
large communications and does not seem efficient after all... Maybe we can think of another 
approach that would take into account both data size and bottom level...}
\AB{I can further detail if needed, moving data of $\PD_j$ from $\curM_j$
to $\curC_j$, and removing it from $\PD_j$...}
If we still do not have enough memory after having tentatively evicted all files from $\PD_j$,
we set the finish time to~$+\infty$ (invalid choice).

\smallskip
\noindent{\bf Step 3.} We tentatively assign task~$v$ on $p_j$. Its starting time $st_v$
is dictated by the maximum between $rt_j$, and all communications that
must be orchestrated from predecessor tasks $u\notin T(p_j)$. Its
finish time on $p_j$ is then 
$FT(v,p_j) = st_v + \frac{w_v}{s_j}$.

\medskip
\noindent{\em Assignment of task~$v$.}\\
Once we have computed all finish times for task~$v$, 
we keep the minimum $FT(v,p_j)$ and assign task~$v$
to processor~$p_j$, updating $\MM_j$ and $\MC_j$ as needed,
as well as all the $rt$ values for $p_j$ and the communication channels.

>>>>

\subsection{Heuristics}
    Like the original HEFT, our heuristic consistst of two steps: first, computing task ranks,
    and second, assigning tasks to processors in the order defined in the first step.
    We consider three variants of HEFT accounting for memory usage, which only
    differ in the order they consider tasks to be scheduled.

\subsubsection{Step 1: calculate task ranks}

@@

HEFTM-MM orders tasks as dictated by MinMem.

\subsubsection{Task assignment}

@@

\smallskip
\noindent{\bf Step 2.} Next, we check the memory constraint on~$p_j$, by computing
\[Res = \curM_j  - m_v + \sum_{u \in Pred(v), u\notin T(p_j)}  \{c_{u,v}\}
- \sum_{w\in Succ(v)}  \{c_{v,w}\}.\]

$T(p_j)$ is the set of tasks already scheduled on $p_j$; by step 1, their files are
already in the memory of~$p_j$. However, the files from the 
other predecessor tasks must be loaded in memory before executing task~$v$,
as well as $m_v$ and the data generated for all successor tasks.
$Res$ is then checking whether there was enough memory; if it is negative,
it means that we have exceeded the memory of~$p_j$ with this tentative 
assignment.

In this case ($Res <0$), we  try evicting
some data from memory so that we have enough memory to execute task~$v$. 
We need to evict at least $Res$ data.
For now, we propose a greedy approach, evicting the smallest files of $\PD_j$ until $Res$ data has been evicted,
in order to avoid costly communications. 
\AB{FYI We initially discussed  evicting the largest files, but this leads to 
large communications and does not seem efficient after all... Maybe we can think of another 
approach that would take into account both data size and bottom level...}
While tentatively evicting files, we remove them from the list of pending memories and move them into a list
    of memories pending in the communication buffer.
We keep track of the available buffer size, too.

If we still do not have enough memory after having tentatively evicted all files from $\PD_j$,
    or if while doing so we exceeded the size of the available buffer,
we set the finish time to~$+\infty$ (invalid choice).

\smallskip
\noindent{\bf Step 3.} We tentatively assign task~$v$ on $p_j$. Its starting time $st_v$
is dictated by the maximum between $rt_j$, and all communications that
must be orchestrated from predecessor tasks $u\notin T(p_j)$. Its
finish time on $p_j$ is then 
$FT(v,p_j) = st_v + \frac{w_v}{s_j}$.
    \skug {TODO PUT THE FORMULA HERE}

\medskip
\noindent{\em Assignment of task~$v$.}\\
Once we have computed all finish times for task~$v$, 
we keep the minimum $FT(v,p_j)$ and assign task~$v$
to processor~$p_j$.
In detail, we:

    \textbullet
    Evict the memories that need to be evicted to free the memory. We remove these memories from pending memories
        $PD_j$, add them to pending data in the communication buffer, and reduce the available buffer size accordingly.

    \textbullet For every predecessor of~$v$ that has been assigned to another processor, we

    \textbullet We compute the correct amount of available memory for $p_j$ (for when the task is done).
For each predecessor that is mapped to the same processor, we remove the pending memory corresponding to the weight of
    the incoming edge, also freeing the same amount of available memory (increasing $CurM_j$).
For each successor, on the other hand, we add the edge weights to pending memories and reduce $CurM_j$ by the corresponding
    amount.

    \textbullet
We adjust ready times on communication buffers $rt_{j, j'}$ for every predecessor processor $u$ of $v$: we increase them by the
    communication time $c(v, u) / \beta$.

    updating $\MM_j$ and $\MC_j$ as needed,
as well as all the $rt$ values for $p_j$ and the communication channels.
